Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-08 minimax.tex
One more table (whoohoo) and agen instead of voter

This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known. It also permits to obtain a progressively refined recommendation without requiring to achieve full knowledge of either sort of information.
%However, there may be cases where both of them are only partially known.
%This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; voters may need time to form reflective preferences.

Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile. In addition, the preferences of the agents are incrementally acquired by asking comparison queries. 
In this setting, we propose a method for robust approximate winner determination with minimax regret. We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative. Finally, we find out experimentally that questioning voters is more useful than questioning the chair in our setting.
\end{abstract}

@@

\paragraph{Experimental conclusions}
Our approach permits to compare experimentally strategies that question the chair, the voters, or both. We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ agents. First, a good quality recommendation can be reached by asking what can be considered a reasonable number of questions to the chair and agents. For example, in a problem of size $m = 5$, $n = 10$, $55$ questions in total are required to reach a good quality recommendation, whcih can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
Second, the quality of the recommendation increases faster than linearly with the number of questions, after only a few questions (the first few questions yield no increase in quality).
Third, we experimentally find out that asking questions to the agents only performs similarly than asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
%the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered), up to a certain proportion of questions asked to the chair. 
Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.

@@

\section{Social choice with partial information}
\label{sec:background}
We now introduce some basic concepts.
We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents (voters). Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order ${\pref_j}  \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
A profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.

@@

The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the voters first. It is parameterized by $p$, a value indicating the number of questions that must be asked to the chair.
The \strat{Two phases - ca} variant first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ac} variant starts with $k - p$ questions to the agents, then questions the chair. 
%Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule. 
%And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
%This strategy also permits to simulate the current state of the art when considering incomplete preferences. By asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule. Similarly, if we invert to whom ask questions first, we fall instead in an already studied case of uncertainty of the voting rule with a known complete profile.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
\commentOC{
	\begin{enumerate}
		\item Pessimistic VS Elitist
		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. 
		\item find a way of displaying the graph so that it is understandable in B/W.
		\item Time comparison XPess VS Pess?
		\item Check Pess VS XPess on other sizes.
		\item Prop qC in value of information
	\end{enumerate}
}
Our experiments are described by topic here below. We generally use the following protocol, deviations are indicated below for each experiment.

Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each voter is generated independently from the other ones and all have the same probability of appearing. The weights are generated by drawing $m-1$ differences randomly with uniform distribution, normalizing them, then ordering them, in order to ensure convexity.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $p(t) = 1.1$ and $p'(t) = 10^{-6}$ when $t = $“chair” and $p(t) = 1.0$ and $p'(t) = 0$ when $t = $“agent”.

@@

\subsection{Absolute evaluation of Pessimistic strategy}
\label{sec:lowRegret}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
			\toprule
			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
			\midrule
			5 & 10 & 1.0 & 60 &  55 \\
			5 & 15 & 1.5 & 80 &  83 \\
			5 & 20 & 2.0 & 110 &  110 \\
			10 & 20 & 2.0 & 340 &  341 \\
			10 & 30 & 3.0 & 527 &  512 \\
			15 & 30 & 3.0 & 919 &  991 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for various problem sizes.}
	\label{tab:lowRegret}
\end{table}

The previous section compares Pessimistic to other strategies. In this set of experiments, we wonder about the absolute quality of Pessimistic. For practical usability, it is important to know how many questions should be asked in order to reach a low regret level. Here, we consider a low level to be a tenth of the number of voters ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the voters rank $x$ last instead of first.
The results for various sizes are displayed in \cref{tab:lowRegret}. From these numbers, we obtain the function $0.4m^{1.6}n$ as a general approximation formula for the number of questions required to reach a low regret level. We see that the number of questions required grows approximately linearly with the number of voters and grows less fast than the square of the number of alternatives, for the sizes we considered. In other words, on average, assuming no questions get asked to the committee, each voter will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level, if this experimental formula reveals correct. For $m = 5$, that is about $6$ questions per voter; for $m = 10$, that is about $17$ questions per voter; and for $m = 15$, that is about $33$ questions per voter.

@@

%In this work, we advocate obtaining an approximate winner without determining completely the voting rule, or the profile. \Cref{sec:lowRegret} evaluates the number of questions per voter required to reach a low regret value.
%In this section we want to explore to which extent it is possible to recommend without knowing the voting rule. One extreme, in our setting, consists in knowing only that the weights are convex, our basis hypothesis. The

>>>>

This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known. It also permits to obtain a progressively refined recommendation without requiring to achieve full knowledge of either sort of information.
%However, there may be cases where both of them are only partially known.
%This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; agents may need time to form reflective preferences.

Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile. In addition, the preferences of the agents are incrementally acquired by asking comparison queries. 
In this setting, we propose a method for robust approximate winner determination with minimax regret. We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative. Finally, we find out experimentally that questioning agents is more useful than questioning the chair in our setting.
\end{abstract}

@@

\paragraph{Experimental conclusions}
Our approach permits to compare experimentally strategies that question the chair, the agents, or both. We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ agents. First, a good quality recommendation can be reached by asking what can be considered a reasonable number of questions to the chair and agents. For example, in a problem of size $m = 5$, $n = 10$, $55$ questions in total are required to reach a good quality recommendation, whcih can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
Second, the quality of the recommendation increases faster than linearly with the number of questions, after only a few questions (the first few questions yield no increase in quality).
Third, we experimentally find out that asking questions to the agents only performs similarly than asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
%the value of information of one question to the chair is similar to the value of information of one question to a agent (in the ranges we considered), up to a certain proportion of questions asked to the chair. 
Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.

@@

\section{Social choice with partial information}
\label{sec:background}
We now introduce some basic concepts.
We consider a set $A$ of $m$ alternatives (products, restaurants, movies, public projects, job candidates, etc.) and a set $\set{1, …, n}$ of agents. Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order ${\pref_j}  \in \linors$ which is a linear order (a connected, transitive, asymmetric relation) over the alternatives.
Following the social choice nomenclature, we call {\em profile} the association of a preference to each agent, considering a subset of agents from the set $\N$, and denote a profile by $(\pref_1,\ldots,\pref_n)$.
A profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.

@@

The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the agents first. It is parameterized by $p$, a value indicating the number of questions that must be asked to the chair.
The \strat{Two phases - ca} variant first asks $p$ questions to the chair, then $k-p$ questions to the agents, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ac} variant starts with $k - p$ questions to the agents, then questions the chair. 
%Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule. 
%And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
%This strategy also permits to simulate the current state of the art when considering incomplete preferences. By asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule. Similarly, if we invert to whom ask questions first, we fall instead in an already studied case of uncertainty of the voting rule with a known complete profile.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
\commentOC{
	\begin{enumerate}
		\item Pessimistic VS Elitist
		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. 
		\item find a way of displaying the graph so that it is understandable in B/W.
		\item Time comparison XPess VS Pess?
		\item Check Pess VS XPess on other sizes.
		\item Prop qC in value of information
		\item Fix approximation formula
	\end{enumerate}
}
Our experiments are described by topic here below. We generally use the following protocol, deviations are indicated below for each experiment.

Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. The weights are generated by drawing $m-1$ differences randomly with uniform distribution, normalizing them, then ordering them, in order to ensure convexity.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $p(t) = 1.1$ and $p'(t) = 10^{-6}$ when $t = $“chair” and $p(t) = 1.0$ and $p'(t) = 0$ when $t = $“agent”.

@@

\subsection{Absolute evaluation of Pessimistic strategy}
\label{sec:lowRegret}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
			\toprule
			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
			\midrule
			5 & 10 & 1.0 & 60 &  55 \\
			5 & 15 & 1.5 & 80 &  83 \\
			5 & 20 & 2.0 & 110 &  110 \\
			10 & 20 & 2.0 & 340 &  341 \\
			10 & 30 & 3.0 & 527 &  512 \\
			15 & 30 & 3.0 & 919 &  991 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for various problem sizes.}
	\label{tab:lowRegret}
\end{table}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=2]}
			\toprule
			m & k \\
			\midrule
			5 & 6.6\\
			10 & 24.8\\
			15 & \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
	\label{tab:fullProfile}
\end{table}

The previous section compares Pessimistic to other strategies. In this set of experiments, we wonder about the absolute quality of Pessimistic. For practical usability, it is important to know how many questions should be asked in order to reach a low regret level. Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
The results for various sizes are displayed in \cref{tab:lowRegret}. 
By relating the sizes to the column $k_{\MMR}$, we obtain the function $0.4m^{1.6}n$ as an approximation formula for the number of questions required to reach a low regret level. We see that the number of questions required grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered. In other words, on average, assuming no questions get asked to the committee, each agent will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level, if this experimental formula reveals correct. For $m = 5$, that is about $6$ questions per agent; for $m = 10$, that is about $17$ questions per agent; and for $m = 15$, that is about $33$ questions per agent. These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}. We constrained the Pessimistic strategy to ask questions to the agent only, and ran it on a single agent problem, with various values for $m$, to evaluate the number of questions required to elicit the full preference of an agent.

@@

%In this work, we advocate obtaining an approximate winner without determining completely the voting rule, or the profile. \Cref{sec:lowRegret} evaluates the number of questions per agent required to reach a low regret value.
%In this section we want to explore to which extent it is possible to recommend without knowing the voting rule. One extreme, in our setting, consists in knowing only that the weights are convex, our basis hypothesis. The
